MaxEnt: What is it good for?

### 2015-06-26 ms.tex
Caption
Relate 'updating given propositions' to expected values

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{distribution.pdf}
\caption{\label{fig:distribution}}
\end{center}
\end{figure}

@@

\begin{eqnarray}
P(D) = 1
\end{eqnarray}
where $D$ is a proposition about the value of $x$. For example, consider
updating from the prior $q(x)$ shown in Figure~\ref{fig:distribution}, to
a posterior $p(x)$, using the testable information
\begin{eqnarray}
P(3 \leq x \leq 5) = 1.
\end{eqnarray}

Clearly, the distribution $q(x)$ doesn't satisfy this constraint, so we
need to update to a new distribution $p(x)$ using MaxEnt.

>>>>

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{distribution.pdf}
\caption{A prior distribution $q(x)$, which we will use
update to a posterior $p(x)$ given different kinds of testable information.
\label{fig:distribution}}
\end{center}
\end{figure}

@@

\begin{eqnarray}
P(D) = 1
\end{eqnarray}
where $D$ is a proposition about the value of $x$. For example, consider
updating from the prior $q(x)$ shown in Figure~\ref{fig:distribution}, to
a posterior $p(x)$, using the testable information
\begin{eqnarray}
P(3 \leq x \leq 5) = 1.\label{eq:prob_one}
\end{eqnarray}
Clearly, the distribution $q(x)$ doesn't satisfy this constraint. According
to $q(x)$ the probability that $x$ is 3, 4, or 5 is 0.225, not 1.
Therefore, we
need to update to a new distribution $p(x)$ using MaxEnt. It may not be
immediately obvious, but Equation~\ref{eq:prob_one} can be viewed as
a constraint on an expected value:
\begin{eqnarray}
\left<
\mathds{1}\left(3 \leq x \leq 5\right)
\right>_p = 1.
\end{eqnarray}
where $\mathds{1}()$ is an indicator function which returns 1 where the
argument is true and 0 where it is false. This allows us to use the
result for expected value constraints, given in
Section~\ref{sec:expectations}.
